### 2020-02-02 thesis/paper.tex
minor edit

\part{Implemented Tool}
\chapter{Using the Tool}\label{cha:usingtool}
This chapter describes what a user can do with the newly implemented tool.

@@

\section{File Input and Output}
\subsection{Clustering Data}

>>>>

\part{Implemented Tool}
\chapter{Using the Tool}\label{cha:Tool}
This chapter describes what a user can do with the newly implemented tool.

@@

\section{File Input and Output}
Loading and saving data is needed for the tool to make it more usable. For this reason it is possible to not only import data for clustering but also to save workflows and whole groups of clustering results for later reuse.
\subsection{Clustering Data}
